\begin{details}
    \name{Stephen Belcher}
    % include some dynamically-generated data too.
    \immediate\write18{./output-details.bash}\input{outputs/details.tex}
    \email{sbelcher+jobs}{gmail}
    \repo {https://github.com/sycobuny/resume}
\end{details}

\begin{objective}
    To obtain positions suitable to enable continued learning, sharing of new
    knowledge, and growth in the technical community, as well as to facilitate
    the development of new software and technologies.
\end{objective}

\begin{skills}
    \begin{skillCategory}{Computer Languages}
        \skill{
            Ruby, including extensive experience with Ruby on Rails,
            Sinatra/Padrino, and wxRuby.
        }
        \skill{
            Perl, including modern web frameworks like Mojolicious, database
            connection with DBI and internal functions in PL/Perl in
            PostgreSQL. Familiarity with complex regular expressions, and GUI
            development using the Perl/Tk and wxPerl frameworks.
        }
        \skill{
            Various reporting languages and technologies, such as the Prawn
            PDF library for Ruby, \LaTeX, and the XML-based XLST/XSL-FO
            dialects.
        }
        \skill{
            PHP, including developing abstract database model systems and
            simplified testing frameworks for producing readable, reliable and
            maintanable code.
        }
        \skill{
            Visual Basic, particularly with regards to creating automated
            forms in Microsoft Office applications.
        }
        \skill{
            Puppet, Java, C/C++, HTML/HAML, CSS/SASS, JavaScript, Vimscript,
            and Markdown.
        }
    \end{skillCategory}

    \begin{skillCategory}{Database and System Administration}
        \skill{
            Administration of both Linux and FreeBSD server environments,
            including scheduling tasks with cron, setting up web server and
            database server daemon processes, and management of software
            packages and utilities.
        }
        \skill{
            Settng up and managing systems using Puppet, including developing
            custom modules, types, providers, and functions in native Ruby.
            Creation and maintenance of custom rules for managing development
            mirrors of production servers using Vagrant.
        }
        \skill{
            PostgreSQL administration experience, including designing custom
            datatypes, functions, triggers, views, and server tuning and
            creation of automatic management and monitoring scripts.
        }
        \skill{
            Experience designing and implementing databases in MySQL and
            SQLite.
        }
        \skill{
            Familiarity with multiple methods of accessing legacy systems,
            including Microsoft Access and FoxPro.
        }
    \end{skillCategory}

    \begin{skillCategory}{Other}
        \skill{
            Frequent speaker at Baltimore Perl user group meetings. Two years
            speaking at the DC/Baltimore Perl Workshop, covering Sass
            stylesheets and the PL/Perl PostgreSQL procedural language.
        }
        \skill{
            Organizing departmental meetings for IT staff to increase
            cross-staff sharing of knowledge, and coordination of efforts.
        }
        \skill{
            Proficient with using, configuring, and scripting Vim to perform a
            wide variety of tasks quickly and efficiently.
        }
    \end{skillCategory}
\end{skills}

\begin{jobs}
    \jobTitle       {Programmer}
    \jobCompany     {Kelly Services, Inc.}
    \jobDuration    {December 2011}{Present}
    \jobDescription {
        Responsible for maintaining large-scale existing web applications
        using various languages, such as Ruby, Python, PHP and Perl, and
        database engines, such as PostgreSQL and MySQL. This includes fixing
        bugs, patching security holes, as well as adding new feature requests
        from users.

        Designed multiple new websites from the ground up, including meeting
        with stakeholders to assess requirements, create work estimates, and
        develop using modern practices to ensure ease of future maintenance.

        Fostered a culture of good practices, including use of revision
        control for projects and development of open-souce tools to increase
        re-usability of software. Also encouraged strong foundational security
        standards to guarantee applications are written more securely from the
        outset, ensuring greater stability overall.

        Maintained systems using Puppet with custom-written modules, types,
        and classes.
    }

    \jobTitle       {Database Manager}
    \jobCompany     {EBL Engineers, LLC}
    \jobDuration    {June 2005}{Present}
    \jobDescription {
        Work included creating applications for use in maintaining hospital
        accreditation according to continually-updated standards from The
        Joint Commission in service of the NIH's Clinical Research Center.

        Designed a database to represent a hospital facility, its operations
        and staff, including ongoing construction projects, equipment, and
        periodic maintenance. The database includes the ability to monitor the
        facility's temporal evolution through time, taking into account
        modification of physical space over time through construction
        projects.

        Designed and implemented various interfaces to the database, according
        to the evolving needs of the organization. These include server APIs,
        web interfaces, cross-platform GUI controls, and automatic reporting
        to CSV, PDF, and other formats.

        Hired and managed a system administrator/programmer to decrease time
        to develop deliverables and enhance the quality of finished work.
        Worked with the system administrator in developing a set of security
        controls for government standards compliance.
    }

    \jobTitle       {Stage Crew}
    \jobCompany     {Peabody Conseravtory of Music}
    \jobDuration    {September 2003}{May 2005}
    \jobDescription {
        Responsible for setting and striking performances for various chamber,
        orchestra, choral, and other ensemble concerts and recitals.
    }
\end{jobs}

\begin{education}
    \educationDegree      {Bachelor of Music in Harp Performance}
    \educationSchool      {Peabody Conservatory of Music}
    \educationDate        {May 2005}
    \begin{educationAchievements}
        \educationAchievement {
            Studied computer science at parent university Johns Hopkins,
            including coursework on programming, data structures, and
            CPU/Assembler fundamentals.
        }
        \educationAchievement {
            Dean's List.
        }
    \end{educationAchievements}

    \educationDegree      {High School Diploma}
    \educationSchool      {Baltimore School for the Arts}
    \educationDate        {May 2002}
    \begin{educationAchievements}
        \educationAchievement {
            Member of the Daniel Ramos Chapter of the National Honor Society.
        }
    \end{educationAchievements}
\end{education}
